

%from micro2015template:
%%\documentclass{sig-alternate}

\documentclass[10pt,final,conference]{IEEEtran}

% Set letter paper size:

\usepackage[
  pass,% keep layout unchanged 
  % showframe,% show the layout
]{geometry}

\newcommand{\ignore}[1]{}
\usepackage{fancyhdr}
\usepackage[normalem]{ulem}
\usepackage[hyphens]{url}
%\usepackage{hyperref}

% from Yoav's template
\usepackage{xcolor}
\usepackage{graphicx}

%% %%%%%%%%%%%---SETME-----%%%%%%%%%%%%%
%% \newcommand{\microsubmissionnumber}{XXX}
%% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% \fancypagestyle{firstpage}{
%%   \fancyhf{}
%% \setlength{\headheight}{50pt}
%% \renewcommand{\headrulewidth}{0pt}
%%   \fancyhead[C]{\normalsize{MICRO 2016 Submission
%%       \textbf{\#\microsubmissionnumber} -- Confidential Draft -- Do NOT Distribute!!}} 
%%   \pagenumbering{arabic}
%% }  

\usepackage{tabularx}
\usepackage{tabulary}
% more compact + self-contained (with embedded fonts)
\usepackage[T1]{fontenc}
\usepackage[ansinew]{inputenc}
%
%\usepackage[normalem]{ulem}
%\usepackage{titling}            % control the maketitle
%\setlength{\droptitle}{-3.3em}  % This is your set screw
%\usepackage[kerning,spacing]{microtype}
%\microtypecontext{spacing=nonfrench}
\usepackage[caption=false]{subfig}
%\captionsetup{position=top} % put subcations above subfigures
\captionsetup[subfloat]{margin=3pt}

% util
\newcommand{\mypar}[1]{\textbf{#1}\ \ }

% yoav macros
\newcommand{\hide}[1]{}
\setlength{\marginparwidth}{2cm}
%\newcommand{\comment}[1]{\marginpar{\footnotesize #1}}

%\newcommand{\comment}[1]{}
\newcommand{\comment}[1]{\textcolor{red}{[#1]}}

\renewcommand{\tilde}[0]{$\sim$}
\newcommand{\us}[0]{$\mu s$}

\newcommand{\speedup}[1]{#1$\times$}
\newcommand{\percent}[1]{#1\% }

\usepackage{soul,color}

\newcommand{\hlc}[2][yellow]{ {\sethlcolor{#1} \hl{#2}} }

\newcommand{\replace}[2]{
  \hlc[green]{#1}
%  \hlc[red]{#2}
}


%% final micro instructions
\pagenumbering{gobble}
%not sure we need this:
\setlength{\paperheight}{11in}
\setlength{\paperwidth}{8.5in}

\hyphenation{op-tical net-works semi-conduc-tor}

%###############################################################################
\title{NeSC: Self-Virtualizing Nested Storage Controller}
%###############################################################################


%% \author{\IEEEauthorblockN{Yonatan Gottesman$^{1}$ \qquad\qquad\qquad Yoav Etsion$^{1,2}$  \\[0.75ex]}
%%   \IEEEauthorblockA{$^{1}$Electrical Engineering \qquad ${^2}$Computer Science   \\
%%     Technion --- Israel Institute of Technology  \\
%%     \{yonigo,yetsion\}@tce.technion.ac.il
%% }}


\author{
\IEEEauthorblockN{Yonatan Gottesman}
\IEEEauthorblockA{Electrical Engineering\\
  Technion --- Israel Institute of Technology\\
  yoni@tce.technion.ac.il}
\and
\IEEEauthorblockN{Yoav Etsion}
\IEEEauthorblockA{Electrical Engineering and Computer Science\\
  Technion --- Israel Institute of Technology\\
  yetsion@tce.technion.ac.il}
}


%\numberofauthors{1}
%% \author{
%% % You can include any number of authors here,
%% % e.g. one 'row of three' or two rows (consisting of one row of three
%% % and a second row of one, two or three).
%% %
%% % The command \alignauthor (no curly braces needed) should
%% % precede each author name, affiliation/snail-mail address and
%% % e-mail address. Additionally, tag each line of
%% % affiliation/address with \affaddr, and tag the
%% % e-mail address with \email.
%% %
%% % 1st. author
%%   \alignauthor Yonatan Gottesman$^{1}$ \qquad\qquad\qquad Yoav Etsion$^{1,2}$  \\[0.75ex]
%%   \affaddr $^{1}$Electrical Engineering \qquad ${^2}$Computer Science   \\
%%   \affaddr Technion --- Israel Institute of Technology  \\
%%            \email{\{yonigo,yetsion\}@tce.technion.ac.il} 
%% }


%% %###############################################################################
%% \begin{document}
%% \date{}
%% \maketitle

\IEEEoverridecommandlockouts 
\IEEEpubid{\makebox[\columnwidth]{978-1-5090-3508-3/16/\$31.00~\copyright~2016 IEEE \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}

\begin{document}
%\conferenceinfo{MICRO 2016}{Taipei, Taiwan}
\maketitle
\pagestyle{plain}

%###############################################################################
% abstract
%###############################################################################
\begin{abstract}
The emergence of high-speed, multi GB/s storage devices has shifted the performance bottleneck of storage virtualization to the software layers of the hypervisor. The hypervisor overheads can be avoided by allowing the virtual machine (VM) to directly access the storage device (a method known as direct device assignment), but this method voids all protection guarantees provided by  filesystem permissions, since the device has no notion of client isolation.
Recently, following the introduction of 10Gbs and higher networking interfaces, the PCIe specification was extended to include the SR-IOV specification for self-virtualizing devices, which allows a single physical device to present multiple virtual interfaces on the PCIe interconnect. Using SR-IOV, a hypervisor can directly assign a virtual PCIe device interface to each of its VMs. However, as networking interfaces simply multiplex packets sent from/to different clients, the specification does not dictate the semantics of a virtual storage device and how to maintain data isolation in a self-virtualizing device.



  In this paper we present the self-virtualizing, nested storage controller (NeSC) architecture, which includes a filesystem-agnostic protection mechanism that enables the physical device to export files as virtual PCIe storage devices. The protection mechanism maps file offsets to physical blocks and thereby offloads the hypervisor's storage layer functionality to hardware.
  Using NeSC, a hypervisor can securely expose its files as virtual PCIe devices and directly assign them to VMs.
  We have prototyped a 1GB/s NeSC controller using a Virtex-7 FPGA development board connected to the PCIe interconnect. 
  Our evaluation of NeSC on a real system shows that NeSC virtual devices enable VMs to access their data with near-native performance (in terms of both throughput and latency).
\end{abstract}
%###############################################################################
\input{vdisk-intro}
\input{vdisk-motivation}
\input{vdisk-related}
\input{vdisk-design}
\input{vdisk-arch}
\input{vdisk-methodology}
\input{vdisk-eval}
\input{vdisk-conclusions}
\input{acks}

%###############################################################################


%###############################################################################



%###############################################################################

%\small
\bibliographystyle{ieeetr}
\bibliography{macros,vdisk}

\end{document}

